\acknowledgments

I would first express my enormous gratitude to my thesis supervisor Prof. Chii Shang for giving me the opportunity to start my MPhil degress in this research group. I was given chances to expose to different research topics and work with other students, most important, I have learned so much from his mentoring.  He also encourage me to develop the research area I am interested in. I was benefited from his knowledge in this domain and his wisdom in 


I would first express my gratitude to my supervisor Prof. Chii SHANG for giving me patient instruction and continuous support during my MPhil study. He encouraged me to learn from mistakes and move forward in steady steps with new-found wisdom. I benefited a lot from his explicit guidance on critical thinking during research and teaching. He has been an excellent mentor and I sincerely appreciate the opportunity to work with him.

I really appreciate Prof. Guanghao CHEN and Prof. Bo SUN for serving on my thesis examination committee. Special thanks should go to Mr. Ran YIN and Miss. Yingying XIANG for giving critical and constructive suggestions on my research.

Thanks also go to technical staff including Mr. Shing Tak LUI, Mr. Wai Lun Johnson YAU and Mr. Chi Man HO for their assistance in instrumentation operation and maintenance.

With great pleasure, I would like to thank my groupmates, labmates and friends for their assistance and friendship.

Finally, I would like to express my gratitude to my family for their love, support and continuous encouragements.

\endacknowledgments
